---
format: html
execute:
  eval: false
---

## How to install materials

To install the materials locally in your computer you have to follow these instructions:

<ol>
<li> Install the package {CursBioR}

If you don't have the package, you have to install it for the first time:

```{r}
#Install it for the first time:
pak::pak("bruigtp/CursBioR")
```

</li>

<li> Load package and run `install_course()`

This function will download the materials in the path in your computer specified with `destdir`:

```{r}
library(CursBioR)

#Download materials for the 1st session:
install_course(destdir = "<YOUR_PATH/CursBioR>", session = 1)
```

Remember that R can't read Windows backslash in paths: `\`. We have to manually change all the `\` for the `/` in a path:

 - Incorrect: `C:\Users\username\Documents\CursBioR`

 - Correct: `C:/Users/username/Documents/CursBioR`

</li>

<li> Repeat the previous step for a new session

This step will have to be repeated every week each time new material will be uploaded:

```{r}
library(CursBioR)

#Download materials for the 2nd session:
install_course(destdir = "<YOUR_PATH/CursBioR>", session = 2)
```

</li>
</ol>